\Large \bf Vigor: Toward Carrier-Grade Software Network Functions

### 2016-10-24 doc/paper/paper.tex
Continuation of the paper example (draft, of course).

@@

The Vigor library comes with a formal specification and a formal proof that the implementation satisfies that specification (we show neither of them here, due to space constraints). In other words, there is a formal spec for \code{ring} and a proof that the \code{ring} implementation satisfies the spec. This is how we enable SE to verify the high level code, while using separation logic to verify the library of components---two different verifications techniques for two different parts of the NF. Doing the library verification requires deep expertise in program verification, but our effort is amortized across all NFs that use the library. Vigor makes it possible for NF developers to verify their code without having to understand verification. Note that stating invariants for dataplane software turns out to require no verification expertise.

@@

>>>>

Suppose we had an overapproximate model:
\begin{lstlisting}
void ring_pop_front(struct ring* r,
                    struct packet* p) {
  FILL_SYMBOLIC(p, sizeof(struct packet),
                "popped_packet");
}
\end{lstlisting}
Then the \code{ASSERT} would fail.

@@

The Vigor library comes with a formal specification and a formal proof that the implementation satisfies that specification. In other words, there is a formal spec for \code{ring} and a proof that the \code{ring} implementation satisfies the spec. This is how we enable SE to verify the high level code, while using separation logic to verify the library of components---two different verifications techniques for two different parts of the NF. Doing the library verification requires deep expertise in program verification, but our effort is amortized across all NFs that use the library. Vigor makes it possible for NF developers to verify their code without having to understand verification. Note that stating invariants for dataplane software turns out to require no verification expertise.

Here is the example of the proven specification for the function
\code{ring_pop_front}. We do not include the proof of this specification due to
space constraints:

\begin{lstlisting}
void ring_pop_front(struct ring* r,
                    struct packet* p);
/*@ requires ringp(r, ?lst) &*&
             lst != nil &*&
             p->port |-> _ &*&
             struct_packet_padding(p); @*/
/*@ ensures ringp(r, tail(lst)) &*&
            pktp(p, head(lst)); @*/
\end{lstlisting}

Note \code{pktp(p, head(lst));} predicate includes the \code{p->port != 9} property.

@@

To validate the model fit for the particular use case, SEE dumps
all the call sequences (30 in this case) that may happen during the execution.
Vigor checks whether the symbolic model enumerated all the possible
outputs for each sequence.

You can see the example call sequence below. It starts with
\code{loop_invariant_produce} that marks the beginning of a loop iteration. It
continues then with calls to \code{ring_full} \code{ring_empty}, noting that
both return \code{false}. The seqeunce ends with a call to
\code{ring_pop_front}, formally specified above. The last line checks that the
value returned by model (\code{arg2.port != 9}) covers all the cases prescribed
by the specification.

\begin{lstlisting}
int port_0;
struct ring* arg1;
struct packet arg2;
//@ assume((9 == port_0));
arg2.port = port_0;
loop_invariant_produce(&(arg1));
bool ret1 = ring_full(arg1);
//@ assume(ret1 == false);
bool ret2 = ring_empty(arg1);
//@ assume(ret2 == false);

ring_pop_front(arg1, &(arg2));
//@ open pktp(&(arg2), _);
/*@ assert((false == (9 == arg2.port))); @*/
\end{lstlisting}

Suppose we had an underapproximate model:
\begin{lstlisting}
void ring_pop_front(struct ring* r,
                    struct packet* p) {
  p->port = 0;
}
\end{lstlisting}
then the last line in the call sequence check will look like:
\begin{lstlisting}
/*@ assert(0 == arg2.port); @*/
\end{lstlisting}
And the formal verification will fail, because specification admits a wider
range of possible outputs.
